Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
updates
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60909 72bbbca6-d526-0410-a7d9-f06f51895060

% simple tokens
% multiword units
% copula
% clitics
% productive suffixes -lı (cite wafflelazor)

>>>>

Tokenisation of the corpus is performed by our morphological analyser. This analyser
performs tokenisation on the basis of a left-to-right longest match algorithm described
in \textcite{garrido02}. Simple tokens such as \emph{толқулар} `riots' are maintained
as a single token, and their lemma and morphological analysis is returned. Multiword
units such as \emph{ауа райы} `weather' and \emph{ата-ананың} `of parents' are combined
into a single token. Abbreviations and numerals which bear case, such as АҚШ-пен `with the USA'
and \emph{90\%-ына} `to the 90\%' are analysed as a single token, as are light-verbs such as
\emph{пайда бол} `to appear' and tense forms written with space like \emph{оқыған жоқ},
the third-person negative past of \emph{оқы} `to learn'.

In some cases a single token is split into two tokens, as with the aorist copula suffixes,
\emph{үйдемін} `I am in the house' is tokenised as үй.{\sc loc} + е.{\sc cop.aor.sg1}. Furthermore
two input tokens may result in three output tokens, \emph{бар ма?} `is there?' would be
tokenised as бар.{\sc adj} + е.{\sc cop.aor.sg1} + ма.{\sc qst}.

% productive suffixes -lı (cite wafflelazor)
